The evolution of gene expression in the term placenta of viviparous mammals

### 2015-10-21 manuscript/manuscript.Rnw
don't output decimals for FPKM
switch to table from wraptable for now
add PRSS16 gene tree

    if (complete) {
        return(paste0("\\textit{",gene,"}=",
                      formatC(fpkm,digits=2,format="f"),
                      " \\ac{FPKM}"
                      ))
    } else {
        return(fpkm)
    }
}

@@

\begin{wraptable}{R}{0.3\textwidth}
  \tiny
<<top.50.human.expressed.genes,echo=FALSE,results="asis">>=
top.human.genes <- top.genes.table(species.name="homo sapiens")
print(xtable(top.human.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.human.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not
  ribosomal, mitochondrial, or a housekeeping gene in \textit{Homo
    sapiens}}
\label{tab:top50_human_placenta}
\end{wraptable}

@@

\begin{wraptable}{L}{0.3\textwidth}
  \tiny
<<top.50.bonobo.expressed.genes,echo=FALSE,results="asis">>=
top.bonobo.genes <- top.genes.table(species.name="pan paniscus")
print(xtable(top.bonobo.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.bonobo.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Pan paniscus}}
\label{tab:top50_bonobo_placenta}
\end{wraptable}

@@

\begin{wraptable}{R}{0.3\textwidth}
  \tiny
<<top.50.spider.monkey.expressed.genes,echo=FALSE,results="asis">>=
top.spider.monkey.genes <- top.genes.table(species.name="ateles fusciceps")
print(xtable(top.spider.monkey.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.spider.monkey.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Ateles fusciceps}}
\label{tab:top50_spider_monkey_placenta}
\end{wraptable}

@@

\begin{wraptable}{R}{0.3\textwidth}
  \tiny
<<top.50.dog.expressed.genes,echo=FALSE,results="asis">>=
top.dog.genes <- top.genes.table(species.name="canis familiaris")
print(xtable(top.dog.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.dog.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Canis familiaris}}
\label{tab:top50_dog_placenta}
\end{wraptable}

@@

\begin{wraptable}{L}{0.3\textwidth}
  \tiny
<<top.50.cow.expressed.genes,echo=FALSE,results="asis">>=
top.cow.genes <- top.genes.table(species.name="bos taurus")
print(xtable(top.cow.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.cow.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Bos taurus}}
\label{tab:top50_cow_placenta}
\end{wraptable}

@@

\begin{wraptable}{L}{0.3\textwidth}
  \tiny
<<top.50.elephant.expressed.genes,echo=FALSE,results="asis">>=
top.elephant.genes <- top.genes.table(species.name="loxodonta africana")
print(xtable(top.elephant.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.elephant.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Loxodonta africana}}
\label{tab:top50_elphant_placenta}
\end{wraptable}

@@

\begin{wraptable}{L}{0.3\textwidth}
  \tiny
<<top.50.opossum.expressed.genes,echo=FALSE,results="asis">>=
top.opossum.genes <- top.genes.table(species.name="monodelphis domestica")
print(xtable(top.opossum.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.opossum.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Monodelphis domestica}}
\label{tab:top50_opossum_placenta}
\end{wraptable}

@@

>>>>

    if (complete) {
        return(paste0("\\textit{",gene,"}=",
                      formatC(fpkm,digits=0,format="f"),
                      " \\ac{FPKM}"
                      ))
    } else {
        return(fpkm)
    }
}

@@

\begin{table}
  \tiny
<<top.50.human.expressed.genes,echo=FALSE,results="asis">>=
top.human.genes <- top.genes.table(species.name="homo sapiens")
print(xtable(top.human.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.human.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not
  ribosomal, mitochondrial, or a housekeeping gene in \textit{Homo
    sapiens}}
\label{tab:top50_human_placenta}
\end{table}

@@

\begin{table}
  \tiny
<<top.50.bonobo.expressed.genes,echo=FALSE,results="asis">>=
top.bonobo.genes <- top.genes.table(species.name="pan paniscus")
print(xtable(top.bonobo.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.bonobo.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Pan paniscus}}
\label{tab:top50_bonobo_placenta}
\end{table}

@@

\begin{table}
  \tiny
<<top.50.spider.monkey.expressed.genes,echo=FALSE,results="asis">>=
top.spider.monkey.genes <- top.genes.table(species.name="ateles fusciceps")
print(xtable(top.spider.monkey.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.spider.monkey.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Ateles fusciceps}}
\label{tab:top50_spider_monkey_placenta}
\end{table}

@@

\begin{table}
  \tiny
<<top.50.dog.expressed.genes,echo=FALSE,results="asis">>=
top.dog.genes <- top.genes.table(species.name="canis familiaris")
print(xtable(top.dog.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.dog.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Canis familiaris}}
\label{tab:top50_dog_placenta}
\end{table}

@@

\begin{table}
  \tiny
<<top.50.cow.expressed.genes,echo=FALSE,results="asis">>=
top.cow.genes <- top.genes.table(species.name="bos taurus")
print(xtable(top.cow.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.cow.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Bos taurus}}
\label{tab:top50_cow_placenta}
\end{table}

@@

\begin{table}
\tiny
<<top.50.elephant.expressed.genes,echo=FALSE,results="asis">>=
top.elephant.genes <- top.genes.table(species.name="loxodonta africana")
print(xtable(top.elephant.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.elephant.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Loxodonta africana}}
\label{tab:top50_elphant_placenta}
\end{table}

@@

\begin{table}
  \tiny
<<top.50.opossum.expressed.genes,echo=FALSE,results="asis">>=
top.opossum.genes <- top.genes.table(species.name="monodelphis domestica")
print(xtable(top.opossum.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.opossum.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Monodelphis domestica}}
\label{tab:top50_opossum_placenta}
\end{table}

@@

\begin{figure}
<<prss16.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="PRSS16" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression)
@ 
\caption{Expression of \textit{PRSS16} and related genes}
\label{fig:prss16_evolution_tree}
\end{figure}
